Reproduction of Civic Honesty around the Globe

### 2021-03-24 outputs/paper/paper.Rmd
Fix typos

To run the OLS model, we used the @citeR inbuilt function, lm(), which is used to fit linear models. It has two key arguments: formula, and data. Formula takes on the form y ~ x1 + x2, where y is the dependent variable and x1, x2, and onward are the independent variable, while data is the data frame containing the columns specified in the formula. The `stargazer` package by @citeStargazer was used to create the LaTeX regression tables.

@@

Table 1’s results are aggregated across the 40 countries visited to conduct the experiment. Results show the following:
* Lost wallet reporting rates increase by 12 percentage points in the Money relative to the NoMoney condition.
* Men are less likely to report a wallet than women 
the presence of a computer increased likelihood of reporting the lost wallet.
* But, the presence of other bystanders decreased reporting rates.
* However, unlike in the original paper, age groups (above and under 40), and the presence of coworkers had no statistical significance regarding reporting or failing to report lost wallets.

>>>>

To run the OLS model, we used the @citeR inbuilt function, lm(), which is used to fit linear models. It has two key arguments: formula, and data. Formula takes on the form y ~ x1 + x2, where y is the dependent variable and x1, x2, and onward are the independent variable, while data is the data frame containing the columns specified in the formula. The `stargazer` package by @citeStargazer was used to create the LaTeX regression tables. And, the `knitr` package is used to format this paper [@citeKnitr].

@@

Table 1’s results are aggregated across the 40 countries visited to conduct the experiment. Results show the following:

* Lost wallet reporting rates increase by 12 percentage points in the Money relative to the NoMoney condition.
* Men are less likely to report a wallet than women 
the presence of a computer increased likelihood of reporting the lost wallet.
* But, the presence of other bystanders decreased reporting rates.
& However, unlike in the original paper, age groups (above and under 40), and the presence of coworkers had no statistical significance regarding reporting or failing to report lost wallets.
